Cannibalism among the supermassive black holes

### 2016-08-12 paper.tex
worked on Galaxy Background Potential section.

- We implemented the SO potential-density pair (using the m200, r200 from the fitting functions above, getting half-mass radius from NFW profile, and using it as half-mass radius for the SO profile).

@@

\subsubsection{Galaxy background potential}

>>>>

@@

\subsubsection{Galaxy background potential}
The simulations from which we obtained the merger tree data considered only dark matter distributions and were run using the Navarro-Frenk-White (NFW) profile described in \citet{1997ApJ...490..493N}.  Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.  Therefore, NFW background potential was less suitable for our application.

In considering a suitable potential-density pair, characteristics that were important were:
\begin{itemize}
\item It must take into account baryonic mater
\item It must have a finite density in the center out to a scale radius
\item Declining density that drops more sharply out to a second scale radius
\item An even sharper decline in density beyond the second scale radius
\item It must be easily parametrized and written in analytic, closed form
\end{itemize}

For our simulations, the Jerry profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, was used.  In order to fully parametrize the Jerry profile so as to use it in our simulations, we needed to match the stellar and halo mass data from the Kulier et al simulations, to the velocity dispersion at the galaxy's effective radius.  In Kulier's simulations, a galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
\begin{equation}
R_{e} = 2.5 kpc\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98}
\end{equation}
\begin{equation}
\sigma(R_{e}) = 190km/s\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47}
\end{equation}

Given the galaxy's stellar mass $M_{*}$ at redshift z from Kulier's simulations, we can calculate the effective radius and velocity dispersion.  We can then equate these values to the analytic expressions for $\sigma(R_{e})$ in the Jerry profile.  Using a core radius $r_c$ = 100, we can solve for the halo radius $r_h$ using a simple recursive Newton method.  Whether $\sigma_{near}$ or $\sigma_{far}$ is used is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.
